Sketch Recognition and Understanding

### 2009-08-18 trunk/draft/ChapterIntroduction.tex
After all edit

Sketch recognition is divided into three steps: preprocessing, segmentation and symbol recognition. The preprocessing phase captures user input stroke points and collects basic information about the stroke then proceeds to remove noise and compute basic statistical and geometrical information. In the segmentation phase, the strokes are divided into a set of simple geometrical primitives or segments. In the third phase, sketch recognition, strokes and segments are clustered to formulate symbols that can be recognized by a classifier system.
There are several problems in this research area that need to be handled to implement an integrated sketch recognition system. The fact that the user draws strokes in a spontaneous and ambiguous manner intensifies the challenges. One of the main problems is segmenting spontaneous strokes drawn by the user into geometrical primitive segments. Another major problem is the high level of ambiguities in the drawing. The next sections describe each problem in details.

@@

The ambiguities in sketch understanding are found at many levels in the system. Firstly, in the segmentation phase, a single stroke can be interpreted as an ellipse or as a circle. Symbol ambiguity is another problem as a symbol can have more than one interpolation. Due to the user's sloppy drawing the symbols can have more than one interpolation which varies with the domain drawn in it. A similar problem was faced in handwriting recognition (Figure \ref{fig:VorU}). The problem could be solved by providing context or domain information which could not be provided in most sketches. 
\begin{figure}	
	\centering
		\includegraphics[scale=0.65]{../../neededfiles/Figures/VorU.eps}
	\caption[Handwriting Ambiguities] { The same letter can be interpreted differently in various contexts; first as V in drive or as U in Cut. This example is adapted from \cite{Ambiguity}.}
\label{fig:VorU}
\end{figure}

>>>>

Similar to most recognition system, sketch recognition is divided into three steps: preprocessing, segmentation and symbol recognition. The preprocessing phase captures user input stroke points and collects basic information about the stroke then proceeds to remove noise and compute basic statistical and geometrical information. In the segmentation phase, the strokes are divided into a set of simple geometrical primitives or segments. In the third phase, sketch recognition, strokes and segments are clustered to formulate symbols that can be recognized by a classifier system.
There are several problems in this research area that need to be handled to implement an integrated sketch recognition system. The fact that the user draws strokes in a spontaneous and ambiguous manner intensifies the challenges. One of the main problems is segmenting spontaneous strokes drawn by the user into geometrical primitive segments. Another major problem is the high level of ambiguities in the drawing. The next sections describe each problem in details.

@@

The ambiguities in sketch understanding are found at many levels in the system. Firstly, in the segmentation phase, a single stroke can be interpreted as an ellipse or as a circle. Symbol ambiguity is another problem as a symbol can have more than one interpolation. Due to the user's sloppy drawing the symbols can have more than one interpolation which varies with the domain drawn in it. A similar problem was faced in handwriting recognition (Figure \ref{fig:VorU}). The problem could be solved by providing context or domain information which could not be provided in most sketches.

\begin{figure}	
	\centering
		\includegraphics[scale=0.65]{afterDefense/Amb.jpg.eps}
	\caption[Handwriting Ambiguities] {The same handwriting can be interpreted differently in various contexts; In the first line the b can be viewed as a B and in the second one could see it as 8.}
\label{fig:VorU}
\end{figure}
